Appendix

### 2022-02-12 writing/Manuscript_2022.Rmd
latest ms draft edits

To follow up on this effect of site, we tested two potential sources of variation: visuomotor control and effort. 
Insofar as differences in visuomotor control could explain differences between groups, we reasoned that this would manifest as a difference in tracing ability that predicts variation in drawing recognizability. 
Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average (Figure \ref{fig:tracing}), although individual tracing scores were strong predictors of the recognizablity of their own drawings, as in prior work [@long2021parallel]. 
Next, we evaluated whether there were systematic differences in effort between the two groups, as measured by the amount of time each child spent producing their drawings and the number of strokes drawn. 
Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.  
We found that children spent more time drawing when prompted with a picture cue than a verbal cue, and that children in the Beijing group spent more time on their drawings than their counterparts in San Jose.

We then included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second generalized linear mixed-effects model (see Statistical Models). 
If effort and/or tracing ability is sufficient to account for the differences between sites, we reasoned that we should no longer observe a main effect of geographical site on drawing recognizability in this expanded statistical model.
Instead, we observed a significant effect of geographical site (see Table 2), even after having accounted for the effect of individual differences in tracing ability. We also found that the amount of time a child spent drawing negatively predicted recognizability -- indicating that spending more time on a drawing did not necessarily result in a more recognizable drawing. Together, these results suggest that these site differences in the ability to produce recognizable drawings are not explained by differences in effort or tracing ability.

**JEFAN QUERY: I noticed that while draw duration was a negative predictor of recognizability, number of strokes was a positive predictor. We comment on the former, but not the latter. Could it be potentially confusing to a reader if we do not mention the latter?**

@@

On the other hand, we discovered that drawing recognizability differed between sites, with children in the Beijing group having produced more recognizable drawings than those in the San Jose group. 
In follow-up analyses, we found that while there was substantial individual variation in tracing ability and effort, these covariates were insufficient to account for differences in drawing recognizability between groups. 
We also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts. 
While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations.
Further systematic measurement of drawing behavior across a wider variety of geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, critical to strongly evaluate causal theories of such variation [@amir2020cross; @carstensen2021investigating; @frank2021variability].
On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of single demographic covariates, such as nationality [@winner1989can; @kuwabara2016cultural].
We have thus made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style [@gernhardt2015cultural; @senzaki2014holistic].

@@

**JEFAN QUERY: We currently do not have a paragraph that expands on the null effect of cue type. Though perhaps we could, for "balance?"**

@@

**JEFAN QUERY: Is there any way to hijack this APA template to force figures/tables to appear in the text close to where they are mentioned, rather than all the way at the end?**

>>>>

To follow up on this effect of site, we tested two potential sources of variation: visuomotor control and effort. 
Insofar as differences in visuomotor control could explain differences between groups, we reasoned that this would manifest as a difference in tracing ability that predicts variation in drawing recognizability. 
Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average (Figure \ref{fig:tracing}), although individual tracing scores were strong predictors of the recognizability of their own drawings, as in prior work [@long2021parallel]. 
Next, we evaluated whether there were systematic differences in effort between the two groups, as measured by the amount of time each child spent producing their drawings and the number of strokes drawn. 
Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.  
We found that children spent more time drawing when prompted with a picture cue than a verbal cue, and that children in the Beijing group spent more time on their drawings than their counterparts in San Jose.

We then included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second generalized linear mixed-effects model (see Statistical Models). 
If effort and/or tracing ability is sufficient to account for the differences between sites, we reasoned that we should no longer observe a main effect of geographical site on drawing recognizability in this expanded statistical model.
Instead, we observed a significant effect of geographical site (see Table 2), even after having accounted for the effect of individual differences in tracing ability as well as effort covariates for each drawing that was produced. Nonetheless, children's tracing abilities were clearly related to the degree they were able to produce recognizable drawings. Together, these results suggest that these site differences in the ability to produce recognizable drawings are not explained by differences in effort or tracing ability.

@@

<!-- Why might we have not observed an effect of cue type? In related work with adults, @yang2021 found that providing adults with photograph cues of these same categories led to more recognizable drawings of object categories. Thus, one possibility is that children have yet to develop the skill -->

We also discovered that drawing recognizability differed between sites, with children in the Beijing group having produced more recognizable drawings than those in the San Jose group. In follow-up analyses, we found that while there was substantial individual variation in tracing ability and effort, these covariates were insufficient to account for differences in drawing recognizability between groups. 
We also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.

While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations. Further systematic measurement of drawing behavior across a wider variety of geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, critical to strongly evaluate causal theories of such variation [@amir2020cross; @carstensen2021investigating; @frank2021variability]. On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of single demographic covariates, such as nationality [@winner1989can; @kuwabara2016cultural]. We have thus made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style [@gernhardt2015cultural; @senzaki2014holistic].

@@

@@
